A Structural and Functional Bioinformatics Study of QTY-designed Retinylidene Proteins

### 2025-04-27 Paper/Source/manuscript.tex
Complete intro and methodology draft. Structure the results and discussion sections.

\keywords{Keyword 1; Keyword 2; Keyword 3}
\begin{abstract}

@@

Retinylidene proteins are photochemically reactive proteins that is bound to or can bind to retinal (vitamin-A aldehyde) as their chromophore \citep{Spudich_2000}. We will use the term ``opsin'' interchangeably with ``retinylidene proteins'', despite that is sometimes refers specifically to the chromophore-free apoprotein. Retinylidene proteins are divided into two groups, animal opsins and microbial opsins, which are evolutionarily distinct but share common features such as haveing 7 transmembrane (TM) domains and a retinal-binding lysine residue \citep{Yee_2013, Spudich_2000}. In this study, we will consider 9 animal opsins and 3 microbial opsins.

\textbf{Animal opsins} are a type of class A GPCR (G-protein coupled receptor), which are characterized by 7 transmembrane domains, the NPxxY motif, and activation of G-proteins through the outward movement of TM6. \citep{Sakmar_2002, Nordstrom_2011, Zhou_2019}. Almost all animal opsins include a lysine residue that forms a Schiff base linkage with retinal \citep{Bownds_1967, Guhmann_2022}. When retinal absorbs a photon, it isomerizes, usually changing from 11-cis to all-trans. The subsequent conformational changes of the protein are well studied using bovine rhodopsin, which changes from dark state to BATHO state, then LUMI, META I, and META II \citep{Okada_2001, Smith_2010}. Proton transfer plays a major role in this process \citep{Mahalingam_2008}. During this process, TM6 characteristically moves outward, activating the G-protein.

In this study, we selected 9 opsins expressed in the human nervous system: OPN1MW (\href{https://www.uniprot.org/uniprotkb/P04001/entry}{P04001}), OPN1LW (\href{https://www.uniprot.org/uniprotkb/P04000/entry}{P04000}), OPN1SW (\href{https://www.uniprot.org/uniprotkb/P03999/entry}{P03999}), OPN2 (\href{https://www.uniprot.org/uniprotkb/P08100/entry}{P08100}), OPN3 (\href{https://www.uniprot.org/uniprotkb/Q9H1Y3/entry}{Q9H1Y3}), OPN4 (\href{https://www.uniprot.org/uniprotkb/Q9UHM6/entry}{Q9UHM6}), OPN5 (\href{https://www.uniprot.org/uniprotkb/Q6U736/entry}{Q6U736}), RGR (\href{https://www.uniprot.org/uniprotkb/P47804/entry}{P47804}) and RRH (\href{https://www.uniprot.org/uniprotkb/O14718/entry}{O14718}). They belong to several evolutionarily distinct families of animal opsins \citep{Terakita_2005, Shichida_2009}.

@@

\textbf{OPN5} (Opsin 5), also known as neuropsin, is activated by blue and ultraviolet A light \citep{Tarttelin_2003, Yamashita_2010}. It is expressed in the retina and contributes to the regulation of light-dependent vascular development \citep{Nguyen_2019} and the photoentrainment in the cornea and retina \citep{Buhr_2015}.

\textbf{RGR} (RPE-retinal GPCR) is expressed in the RPE (Retinal Pigmented Epithelium) and M\"uller cells in the retina \citep{Shen_1994}. Unlike the aforementioned human opsins, RGR preferentially binds all-trans-retinal and may catalyze its isomerization into 11-cis-retinal via a retinochrome-like mechanism \citep{Radu_2008}. It plays a role in light-dependent synthesis of visual chromophore \citep{Radu_2008}.

@@

\textbf{Bacterial opsins} are transmembrane ion pumps or channels \citep{Findlay_1986, Zhang_2011}. They are also 7TM, though this is due to convergent evolution rather than homology \citep{Yee_2013}. The isomerization of retinal is usually from all-trans to 13-cis, different from that in animal opsins \citep{Findlay_1986, Spudich_2000}. Additionally, bacterial opsins often form oligomers to carry out their functions \citep{Taguchi_2023, Gmelin_2007, Shan_2024}.

@@

\textbf{BACR} (Bacteriorhodopsin) is a light-driven proton pump \citep{Oesterhelt_1971}. \textbf{BACH} (Halorhodopsin) is a light-driven chloride pump activated by yellow light \citep{Schobert_1982}. \textbf{ChR2} (Channelrhodopsin 2) is a light-activated sodium channel activated by blue light \citep{Nagel_2003}. BACH and ChR2 are among the first optogenetic tools \citep{Zhang_2007, Han_2007}. BACH is used for inhibition while ChR2 is used for excitation.

We have asked if retinylidene proteins could be redesigned to be more soluble. Retinylidene proteins are all integral membrane proteins with seven transmembrane alpha-helices embedded in a lipid bilayer. Due the hydrophobic properties of transmembrane domains, they are not water-soluble without the aid of detergents.

Bacteriorhodopsin has been the subject of several protein-solubilizing studies, though to limited success \citep{Sirokman_1993, Gibas_1997, Mitra_2002}. Recently, researchers leveraged a neural network, SolubleMPNN, which was built upon ProteinMPNN, to engineer soluble variants of bacteriorhodopsin while maintaining its ligand-binding ability and light-sensing function \citep{Nikolaev_2024}.

Instead of taking a computational approach, we applied the QTY code to systematically engineer water-soluble analogs with reduced hydrophobicity in membrane proteins. There are structural similarities between hydrophobic and polar amino acids: leucine (L) vs glutamine (Q); isoleucine (I)/valine (V) vs threonine (T); and phenylalanine (F) vs tyrosine (Y), as can be observed on high-resolution electron density maps \citep{Zhang_2018, Zhang_2022, Tegler_2020}. This justifies residue replacement of hydrophobic aminoacids with polar ones. We initially applied the QTY (Glutamine, Threonine, Tyrosine) code to design several detergent-free chemokines receptors, all of which retained structural thermal stability and native ligand-binding activities and enzymatic activities despite substantial changes to the transmembrane domain \citep{Zhang_2018, Tegler_2020}. We have also applied the QTY code to design water-soluble GPCRs, including chemokine receptors \citep{Zhang_2018, Qing_2019, Tegler_2020, Skuhersky_2021}, cytokine receptors \citep{Hao_2020}, and olfactory receptors \citep{Skuhersky_2021, Johnsson_2025}.

AlphaFold2 was released by Google DeepMind in July 2021 \citep{Jumper_2021}. It greatly facilitated the study of QTY-designed protein variants. Subsequently, AlphaFold3 was released in May 2024, featuring an enhanced architecture and improved efficiency \citep{Abramson_2024}. Furthermore, AlphaFold3 enabled accurate prediction of complexes of multiple proteins as well as complexes with nucleic acids and certain small molecules. QTY studies have made use of these new features \citep{Chen_2025, Johnsson_2025}.

GROMACS is a molecular dynamics (MD) simulation program released in 1995 \citep{Berendsen_1995}. Its 5.0 version was released in 2015 \citep{Abraham_2015}. GROMACS enables efficient and realistic simulation of biomolecular systems, and it has been used to investigate structural and functional properties of QTY-designed protein variants in various studies \citep{Karagol_2024, Li_Tang_2024, Smorodina_2024, Li_Wang_2024, Johnsson_2025}.

In this paper, we apply the QTY code to redesign 9 human opsins and 3 microbial opsins. We provide the superpositions of the AlphaFold3-predicted hydrophobic native proteins and their water-soluble QTY variants, and experimentally-determined structures when available. We also provide the comparative surface hydrophobicity of the variants. Furthermore, we run MD simulations of native and QTY-designed OPN2 and analyze their response to the 11-cis to all-trans isomerization of the retinal chromophore.

@@

Results

* discuss the QTY code

* describe and explain Table1

* entrance of retinal is posteriori folding, so it is safe that we predict chromophore-free form

* describe and explain Fig1

* describe and explain Fig2
	- I need more discussion here

* describe and explain Fig3

* discuss AlphaFold3 predictions

* describe, explain, discuss MD results (Fig3 and Fig4)
        - no changes to the NPxxY motif or retinal-binding Lys
        - "The ionic environment of the RSB, defined by the residues of the binding pocket, dictates the spectral and kinetic characteristics of each individual protein." - \citep{Fenno_2011}
	- I need more discussion here

* future scopes and potential applications

* conclusion

@@

The native protein sequences for OPN1MW, OPN1LW, OPN1SW, OPN2, OPN3, OPN4, OPN5, RGR, RRH, BACR, BACH, and ChR2 were attained from UniProt (\url{https://www.uniprot.org}). The sequence for ChR2 was truncated according to the experimental structure in RCSB PDB (\href{https://www.rcsb.org/structure/8ZAN}{8ZAN}). The QTY designs were realized through the Protein Solubilizing Server (\url{https://pss.sjtu.edu.cn/}) \citep{Tao_2022}. For ChR2, secondary structure was provided to the server in SS3 format according to the RCSB PDB structure.

@@

We predicted the structures of the native proteins and their QTY variants using the AlphaFold3 website (\url{https://alphafoldserver.com}) \citep{Abramson_2024}. For microbial opsins, the dimers and trimers had identical subunits, i.e., were homodimers and homotrimers. In AlphaFold3, this is achieved by altering the number of protein copies.

@@

PDB files for native protein structures determined experimentally using X-ray diffraction or electron microscopy were taken from RCSB PDB: OPN2 (\href{https://www.rcsb.org/structure/5W0P}{5W0P}), BACR (\href{https://www.rcsb.org/structure/7XJC}{7XJC}), BACH (\href{https://www.rcsb.org/structure/2JAF}{2JAF}), ChR2 (\href{https://www.rcsb.org/structure/8ZAN}{8ZAN}). The AlphaFold3-predicted native and QTY variants were taken directly from the most probable predicted structure. Superpositions were performs via the command ``super'' in PyMOL (\url{https://pymol.org}). We removed unstructured loops at N and C terminals for clarity.

@@

We used PyMOL (\url{https://pymol.org}) to superpose the native predicted protein structures, their QTY variants, and the experimental structures for those proteins where these existed. We then used UCSF ChimeraX (\url{https://www.cgl.ucsf.edu/chimerax/}) to render each protein model with hydrophobicity patches.

@@

All MD simulations and analyses were executed on a desktop computer with Intel Xeon Platinum 8352V Processor, 256GB RAM and 2 NVIDIA GPU (GeForce RTX 4090) with 24GB VRAM each. All MD simulations were conducted using GROMACS 2024.5 \citep{Abraham_2015} with the CHARMM36m all-atom force field \citep{Huang_2017}. Data for retinal were obtained from NAMD Wiki (\url{https://www.ks.uiuc.edu/Research/namd/wiki/index.cgi?RetinalTop} for topology and \url{https://www.ks.uiuc.edu/Research/namd/wiki/index.cgi?RetinalPar} for parameters) and manually integrated into the protein file. Initial structures, configuration files, and command-line codes for the simulations are publicly available at... [ONLINE DATABASE TO BE PREPARED].

Regarding native OPN2, the membrane protein system was constructed using the web-based membrane builder CHARMM-GUI and was downloaded in GROMACS format \citep{Jo_2008, Wu_2014, Lee_2016}. The protein was centered in a rectangular box. The generated membrane models consisted of 40\% POPC, 40\% POPE, 10\% POPS, and 10\% cholesterol, which simulate a rod photoreceptor disk membrane \citep{Albert_2005}. The system was solvated in TIP3P water with 150 mM NaCl. 11-cis-retinal was manually added to the protein files. LINCS constraints was used for constraints and Verlet integrator was used. Electrostatics was handled with Particle Mesh Ewald (PME), with both Coulomb and van der Waals interaction cutoffs set at 1.2 nm. The energy of the system was minimized using the steepest descent until the maximum forces converged below 1000 kJ/mol/nm. The standard six-step CHARMM-GUI NP$\gamma$T equilibration protocol \citep{Jo_2008} was used, with two 125-ps NVT equilibration simulations, and one 125-ps and three 500-ps NP$\gamma$T equilibration simulations. Temperature and pressure were maintained at 303.15 K and 1.0 bar, respectively, using the V-rescale thermostat and C-rescale barostat with surface-tension coupling. Following equilibration, a 10-ns production MD simulation was run. The retinal molecule was then manually switched to the all-trans state by rotating C13 to C15 and bonded hydrogen and methyl groups by 180 degrees around the C11-C12 bond. Energy minimization and equilibration were repeated exactly as before, and then a 200-ns production MD simulation was run.

Regarding QTY-designed OPN2, the system was constructed directly using GROMACS. The protein was centered in a rectangular box with dimensions equivalent to those of the native OPN2. The equilibration involved a sequence of simulations: a 250-ps NVT equilibration, followed by 125-ps and 1500-ps NPT equilibrations, totaling an equilibration duration that matches that of the natural OPN2. All other configurations and parameters are identical to those of the original OPN2.

ANALYSIS METHODS TO BE ADDED.

@@

The data for ... can be found at... [ONLINE DATABASE TO BE PREPARED]

@@

\section*{Acknowledgements}

Thanks to ... for ... [TO BE ADDED]

>>>>

\keywords{hydrophobic to hydrophilic conversion; membrane proteins; protein design; QTY code; water-soluble retinylidene proteins; water-soluble opsins; activation of QTY variants of rhodopsin}
\begin{abstract}

@@

Retinylidene proteins are photochemically reactive proteins that are bound to or can bind to retinal (vitamin A aldehyde) as their chromophore \citep{Spudich_2000}. We will use the term ``opsin'' interchangeably with ``retinylidene protein'', despite the fact that ``opsin'' sometimes refers specifically to the chromophore-free apoprotein. Retinylidene proteins are divided into two groups, animal opsins and microbial opsins, which are evolutionarily distinct but share common characteristics such as having 7 transmembrane (TM) domains and a retinal binding lysine residue \citep{Yee_2013, Spudich_2000}. In this study, we will consider 9 animal opsins and 3 microbial opsins.

\textbf{Animal opsins} are a type of class A GPCR (G-protein coupled receptor), which are characterized by 7 transmembrane domains, the NPxxY motif, and activation of G-proteins through the outward movement of TM6. \citep{Sakmar_2002, Nordstrom_2011, Zhou_2019}. Almost all animal opsins include a lysine residue that forms a Schiff base link with the retinal \citep{Bownds_1967, Guhmann_2022}. When retinal absorbs a photon, it isomerizes, usually changing from 11-cis to all-trans. The subsequent conformational changes of the protein are well studied using bovine rhodopsin, which changes from dark state to BATHO state, then LUMI, META I, and META II \citep{Okada_2001, Smith_2010}. Proton transfer plays a major role in this process \citep{Mahalingam_2008}. During this process, TM6 is characteristically moved outward, activating the G-protein.

In this study, we selected 9 opsins expressed in the human nervous system: OPN1MW (\href{https://www.uniprot.org/uniprotkb/P04001/entry}{P04001}), OPN1LW (\href{https://www.uniprot.org/uniprotkb/P04000/entry}{P04001}), OPN1SW (\href{https://www.uniprot.org/uniprotkb/P03999/entry}{P03999}), OPN2 (\href{https://www.uniprot.org/uniprotkb/P08100/entry}{P04001}), OPN3 (\href{https://www.uniprot.org/uniprotkb/Q9H1Y3/entry}{Q9H1Y3}), OPN4 (\href{https://www.uniprot.org/uniprotkb/Q9UHM6/entry}{Q9UHM6}), OPN5 (\href{https://www.uniprot.org/uniprotkb/Q6U736/entry}{Q6U736}), RGR (\href{https://www.uniprot.org/uniprotkb/P47804/entry}{P47804}) and RRH (\href{https://www.uniprot.org/uniprotkb/O14718/entry}{O14718}). They belong to several evolutionarily distinct families of animal opsins \citep{Terakita_2005, Shichida_2009}.

@@

\textbf{OPN5} (Opsin 5), also known as neuropsin, is activated by blue and ultraviolet A light \citep{Tarttelin_2003, Yamashita_2010}. It is expressed in the retina and contributes to the regulation of light-dependent vascular development \citep{Nguyen_2019} and photoentrainment in the cornea and retina \citep{Buhr_2015}.

\textbf{RGR} (RPE-retinal GPCR) is expressed in RPE (Retinal Pigmented Epithelium) and M\"uller cells in the retina \citep{Shen_1994}. Unlike the aforementioned human opsins, RGR preferentially binds all-trans-retinal and may catalyze its isomerization into 11-cis-retinal via a retinochrome-like mechanism \citep{Radu_2008}. It plays a role in the light-dependent synthesis of visual chromophore \citep{Radu_2008}.

@@

\textbf{Bacterial opsins} are transmembrane ion pumps or channels \citep{Findlay_1986, Zhang_2011}. They are also 7TM, though this is due to convergent evolution rather than homology \citep{Yee_2013}. The isomerization of retinal is usually from all-trans to 13-cis, different from that in animal opsins \citep{Findlay_1986, Spudich_2000}. In addition, bacterial opsins often form oligomers to carry out their functions \citep{Taguchi_2023, Gmelin_2007, Shan_2024}.

@@

\textbf{BACR} (Bacteriorhodopsin) is a light-driven proton pump \citep{Oesterhelt_1971}. \textbf{BACH} (Halorhodopsin) is a light-driven chloride pump activated by yellow light \citep{Schobert_1982}. \textbf{ChR2} (Channelrhodopsin 2) is a light-activated sodium channel activated by blue light \citep{Nagel_2003}. BACH and ChR2 are among the first optogenetic tools \citep{Zhang_2007, Han_2007}. BACH is used for inhibition, while ChR2 is used for excitation.

We have asked if retinylidene proteins could be redesigned to be more soluble. Retinylidene proteins are all integral membrane proteins with seven transmembrane alpha helices embedded in a lipid bilayer. Because of the hydrophobic properties of the transmembrane domains, they are not water-soluble without the aid of detergents.

Bacteriorhodopsin has been the subject of several protein-solubilizing studies, though with limited success \citep{Sirokman_1993, Gibas_1997, Mitra_2002}. Recently, researchers leveraged a neural network, SolubleMPNN, which was built upon ProteinMPNN, to engineer soluble variants of bacteriorhodopsin while maintaining its ligand-binding ability and light-sensing function \citep{Nikolaev_2024}.

Instead of taking a computational approach, we applied the QTY (Glutamine, Threonine, Tyrosine) code to systematically engineer water-soluble analogs with reduced hydrophobicity in membrane proteins. There are structural similarities between hydrophobic and polar amino acids: leucine (L) vs. glutamine (Q); isoleucine (I) / valine (V) vs. threonine (T); and phenylalanine (F) vs. tyrosine (Y), as can be observed on high-resolution electron density maps \citep{Zhang_2018, Zhang_2022, Tegler_2020}. This justifies the replacement of hydrophobic amino acids with polar ones. We initially applied the QTY code to design several detergent-free chemokines receptors, all of which retained structural thermal stability and native ligand-binding activities and enzymatic activities despite substantial changes to the transmembrane domain \citep{Zhang_2018, Tegler_2020}. We have also applied the QTY code to design water-soluble GPCRs, including chemokine receptors \citep{Zhang_2018, Qing_2019, Tegler_2020, Skuhersky_2021}, cytokine receptors \citep{Hao_2020}, and olfactory receptors \citep{Skuhersky_2021, Johnsson_2025}.

AlphaFold2 was released by Google DeepMind in July 2021 \citep{Jumper_2021}. It greatly facilitated the study of QTY-designed protein variants. Subsequently, AlphaFold3 was released in May 2024, featuring improved architecture and improved efficiency \citep{Abramson_2024}. Furthermore, AlphaFold3 enabled the accurate prediction of complexes of multiple proteins, as well as complexes with nucleic acids and certain small molecules. QTY studies have made use of these new features \citep{Chen_2025, Johnsson_2025}.

GROMACS is a molecular dynamics (MD) simulation program released in 1995 \citep{Berendsen_1995}. Its 5.0 version was released in 2015 \citep{Abraham_2015}. GROMACS enables an efficient and realistic simulation of biomolecular systems, and has been used to investigate the structural and functional properties of QTY-designed protein variants in various studies \citep{Karagol_2024, Li_Tang_2024, Smorodina_2024, Li_Wang_2024, Johnsson_2025}.

In this paper, we apply the QTY code to redesign 9 human opsins and 3 microbial opsins. We provide the superpositions of the AlphaFold3-predicted hydrophobic native proteins and their water-soluble QTY variants, and experimentally-determined structures when available. We also provide a comparison of the surface hydrophobicity of the variants. Furthermore, we run MD simulations of native and QTY-designed OPN2 and analyze their response to the 11-cis to all-trans isomerization of the retinal chromophore.

@@

\subsection*{The QTY code}

Discuss the QTY code.

\subsection*{Retinylidene proteins sequence alignments and other characteristics}

Describe and discuss Table~\ref{tb:characteristics} (native and QTY protein characteristics) // NOTE: the binding of retinal is posterior to folding, so it is safe to say that we predicted chromophore-free form (i.e. folding does not rely on retinal).

\subsection*{Superpositions of AlphaFold3-predicted native human opsins, their water-soluble QTY variants, and experimentally determined structures}

Describe and discuss Fig.~\ref{fig:humansup} (AF3 native - AF3 QTY - experimental superpositions of human opsins).

\subsection*{Pairwise superpositions among AlphaFold3-predicted native human opsins and among their water-soluble QTY variants}

Describe and discuss Fig.~\ref{fig:pairwise} (pairwise superpositions of human opsins) // NOTE: the QTY pairwise superpositions roughly maintains the trends in the native superpositions.

\subsection*{Superpositions of AlphaFold3-predicted native microbial opsins, their water-soluble QTY variants, and experimentally determined structures}

Describe and discuss Fig.~\ref{fig:microbialsup} (AF3 native - AF3 QTY - experimental superimpositions of microbial opsins) // NOTE: comment specifically on the formation of dimers and trimers.

\subsection*{Analysis of the hydrophobic surface of native retinylidene proteins and their water-soluble QTY variants}

Describe and discuss Fig.~\ref{fig:hydrophobicity} (surface hydrophobicity).

Discuss the role of AlphaFold3 predictions.

\subsection*{Simulation of 11-cis to all-trans isomerization of retinal in native OPN2 and its QTY variant}

Describe, explain, discuss MD simulation results. // NOTE: there were no changes to the NPxxY motif or retinal-binding Lys; "The ionic environment of the RSB, defined by the residues of the binding pocket, dictates the spectral and kinetic characteristics of each individual protein." \citep{Fenno_2011}, so QTY variant may have different absorption peak.

\subsection*{Future scopes and potential applications}

* Future scopes and potential applications.

\subsection*{Conclusion}

* Conclusion

@@

The native protein sequences for OPN1MW, OPN1LW, OPN1SW, OPN2, OPN3, OPN4, OPN5, RGR, RRH, BACR, BACH, and ChR2 were obtained from UniProt (\url{https://www.uniprot.org}). The sequence for ChR2 was truncated according to the experimental structure in RCSB PDB (\href{https://www.rcsb.org/structure/8ZAN}{8ZAN}). The QTY designs were performed through the Protein Solubilizing Server (\url{https://pss.sjtu.edu.cn/}) \citep{Tao_2022}. For ChR2, the secondary structure was provided to the server in SS3 format according to the RCSB PDB structure.

@@

We predicted the structures of native proteins and their QTY variants using the AlphaFold3 website (\url{https://alphafoldserver.com}) \citep{Abramson_2024}. For microbial opsins, the dimers and trimers had identical subunits, i.e., they were homodimers and homotrimers. In AlphaFold3, this was achieved by altering the number of protein copies.

@@

PDB files for native protein structures determined experimentally by X-ray diffraction or electron microscopy were taken from RCSB PDB: OPN2 (\href{https://www.rcsb.org/structure/5W0P}{5W0P}), BACR (\href{https://www.rcsb.org/structure/7XJC}{7XJC}), BACH (\href{https://www.rcsb.org/structure/2JAF}{2JAF}), ChR2 (\href{https://www.rcsb.org/structure/8ZAN}{8ZAN}). The AlphaFold3-predicted native and QTY variants were taken directly from the most probable predicted structure. Superpositions were performed via the command ``super'' in PyMOL (\url{https://pymol.org}). We remove unstructured loops at the N and C terminals for the sake of clarity.

@@

We used PyMOL (\url{https://pymol.org}) to superpose the native predicted protein structures, their QTY variants, and the experimental structures for the proteins where these existed. We then used UCSF ChimeraX (\url{https://www.cgl.ucsf.edu/chimerax/}) to render each protein model with hydrophobicity patches.

@@

All MD simulations and analyses were executed on a desktop computer with Intel Xeon Platinum 8352V Processor, 256 GB RAM, and 2 NVIDIA GPU (GeForce RTX 4090) with 24 GB VRAM each. All MD simulations were conducted using GROMACS 2024.5 \citep{Abraham_2015} with the CHARMM36m all-atom force field \citep{Huang_2017}. Data for retinal were obtained from NAMD Wiki (\url{https://www.ks.uiuc.edu/Research/namd/wiki/index.cgi?RetinalTop} for topology and \url{https://www.ks.uiuc.edu/Research/namd/wiki/index.cgi?RetinalPar} for parameters) and manually integrated into the protein file. Initial structures, configuration files, and command-line codes for the simulations are publicly available at... [ONLINE DATABASE TO BE PREPARED].

Regarding native OPN2, the membrane protein system was constructed using the web-based membrane builder CHARMM-GUI and was downloaded in GROMACS format \citep{Jo_2008, Wu_2014, Lee_2016}. The protein was centered in a rectangular box. The generated membrane models consisted of 40\% POPC, 40\% POPE, 10\% POPS, and 10\% cholesterol, which simulate a rod photoreceptor disk membrane \citep{Albert_2005}. The system was solvated in TIP3P water with 150 mM NaCl. 11-cis-retinal was manually added to the protein files. LINCS constraints were used for constraints, and Verlet integrator was used. Electrostatics was handled with Particle Mesh Ewald (PME), with both Coulomb and van der Waals interaction cutoffs set at 1.2 nm. The energy of the system was minimized using the steepest descent until the maximum forces converged below 1000 kJ/mol/nm. The standard six-step CHARMM-GUI NP$\gamma$T equilibration protocol \citep{Jo_2008} was used, with two 125-ps NVT equilibration simulations, and one 125-ps and three 500-ps NP$\gamma$T equilibration simulations. Temperature and pressure were maintained at 303.15 K and 1.0 bar, respectively, using the V-rescale thermostat and C-rescale barostat with surface-tension coupling. Following equilibration, a 10-ns production MD simulation was run. The retinal molecule was then manually switched to the all-trans state by rotating C13 to C15 and bonded hydrogen and methyl groups by 180 degrees around the C11-C12 bond. Energy minimization and equilibration were repeated exactly as before, and then a 200-ns production MD simulation was run.

Regarding QTY-designed OPN2, the system was constructed directly using GROMACS. The protein was centered in a rectangular box with dimensions equivalent to those of native OPN2. The equilibration involved a sequence of simulations: a 250-ps NVT equilibration, followed by 125-ps and 1500-ps NPT equilibrations, totaling an equilibration duration that matches that of the natural OPN2. All other configurations and parameters are identical to those of the original OPN2.

[ANALYSIS METHODS OF MD SIMULATION RESULTS, TO BE ADDED.]

@@

The data for... can be found at... [ONLINE DATABASE TO BE PREPARED]

@@

\section*{Acknowledgments}

Thanks to... for... [TO BE ADDED]
